\documentclass[class=exam, crop=false, 12pt]{standalone}
\begin{document}
\begin{enumerate}
\item Be patient
\begin{enumerate}
\item Harkness learning in maths is about developing your knowledge over time. With the right study habits, you will eventually succeed.
\item Don't be cross with yourself or others if you don't get things straightaway. Instead, think about what you can do to help yourself improve.
\end{enumerate}
\item Be honest
\begin{enumerate}
\item If you don't understand something, say.
\item If an explanation isn't helping, ask for greater clarity.
\item If you have worked collaboratively, say so, and acknowledge where your partner may be covering gaps in your knowledge.
\end{enumerate}
\item Interrogate
\begin{enumerate}
\item If you're not sure why something is true, how are you sure that it is true? Make sure you can explain every step as you go along.
\item If you think you have the right answer but aren't sure whether your solution is correct, ask someone else to try to find holes in it for you.
\end{enumerate}
\item Be prepared
\begin{enumerate}
\item It's no fun if everyone is talking about the latest episode of something but you haven't seen it yet. Make sure you have understood what all the questions are asking before you come to class.
\item You might not solve all the problems on the a sheet but you should at least try them out. Draw a diagram, summarize the given information, to try to relate to a problem you have already solved.
\item Assess your own work. If you think you have got a good answer, review it so you know what its strengths and weaknesses are.
\end{enumerate}
\item Catch up
\begin{enumerate}
\item If you miss a lesson, you still need to tackle the assigned problems.
\item If you learn in class how to solve a problem you didn't manage to complete for prep, go back in your own time and re-do it.
\end{enumerate}
\item Be involved
\begin{enumerate}
\item This learning journey is a team effort. You will make better progress if you join in.
\item Nobody likes to ride a tandem when one person won't pedal. Your contributions to class are valuable no matter how much you do or don't understand of the question at hand. Be sure to share your ideas.
\end{enumerate}
\end{enumerate}

\end{document}
