\documentclass[class=exam, crop=false, 12pt]{standalone}
\begin{document}
\begin{enumerate}
\item Be patient
\begin{enumerate}
\item Just because you understand something, doesn't mean everyone else does.
\item If you can't explain what you think you understand, you haven't mastered it yet. If people in your group still don't understand you haven't explained it well enough.
\end{enumerate}
\item Be honest
\begin{enumerate}
\item If someone makes a mistake, point it out kindly.
\item If an explanation isn't helping, ask for greater clarity.
\end{enumerate}
\item Ask, don't tell
\begin{enumerate}
\item People make better deductions when they work something out for themselves.
\item See if you can help someone work something out by asking the right questions.
\end{enumerate}
\item Remember your audience
\begin{enumerate}
\item There's no point in explaining something if you leave your audience behind.
\item Check that they understand by asking them directly, and by asking questions that test their understanding.
\end{enumerate}
\item Answer the right question
\begin{enumerate}
\item When someone asks why something works, give them justification.
\item When someone asks how you knew to do what you did, explain your thinking.
\item Understand that these are different, and try to ask the right question, too.
\end{enumerate}
\item Don't be a jerk
\begin{enumerate}
\item People are more likely to listen to your ideas if you put them across politely.
\item Nobody benefits if you mock someone for making a mistake.
\item Nobody likes a know-it-all.
\end{enumerate}
\end{enumerate}

\end{document}
