\documentclass{Welly_Workbook}

\begin{document}
\noindent This book has been designed to help you master all the required content for Core 1 and \mbox{Core 2}. It is not structured like most maths courses you have previously taken, and you will find it requires a different approach on your part. \\ \linebreak
Each lesson you will be set a number of problems---usually between 8 and 10---to prepare for the next lesson. They should take 40-50 minutes in total. You might not always be able to fully solve all problems, but we expect you to attempt as many as you can. In class, you will be expected to present your solutions and discuss solutions that others have shared. Lessons are your principal opportunity to ask for help on material you couldn't do, so be prepared to ask other students how they solved problems or how they knew what approach to take. Discussion should take about 40 minutes in your lessons, and the remainder of the time will be spent looking at problems from the review exercises.\\ \linebreak
\notebook[-4.6]How you take notes is very much up to you, but we have put icons in the margin whenever we think there is a topic on which you are likely to want to take notes. If you are unsure what you are supposed to have understood from a question, ask your peers.\\ \linebreak
Some questions include references to previous questions in square brackets like this: \mbox{[XXV-4]}. This means that the content of the question follows on from the material in problem 4 from sheet 25. If you don't know straightaway how to tackle the problem you are looking at, you might like to follow the reference to see if it sheds any light on the problem.\\ \linebreak
The back of the book contains a glossary of terms---some familiar, some unfamiliar. Terms that appear in italics in the text appear in the glossary, as do a number of general terms which you are expected to know.\\ \linebreak
Each lesson will involve discussing the problems you have prepared for homework in preparation for the next sheet of problems. Don't try to get ahead, therefore, as it will render the discussion less valuable. If you have spare time and want to do more, it is better to look at old questions and satisfy yourself that you really understand them.\\ \linebreak
You will have a fortnightly test, lasting 40 minutes and worth 30 marks. Use your textbook, or the review exercises provided, to help you prepare. \\ \linebreak
Please complete all your solutions in one place, either in an electronic workbook which is shared with your teacher, or in the notebook provided by your teacher. Although your work will not be taken in for regular assessment, you should always be ready to show it to your teacher.
\end{document}
